### 2020-02-12 ChapterResults/chapterResults.tex
Added: Aura size graphs to results
Updated: Description for aura size graphs and predictions

\subsubsection{Experiment parameters and output}
The two servers use the following tolerances unless otherwise stated: a maximum speed tolerance of $32m\mathord{\cdot}s^{-1}$; maximum latency tolerance of $2ms$; and a maximum frame-time tolerance of $15ms$. Each server has a random delay before starting between $0$ and the target frame-time in order to prevent the two servers always having synchronous update cycles. Each experiment is repeated $50$ times. An experiment was carried out for each aura tolerance value, for each experiment, three tolerances values were chosen. For each tolerance value, the following graphs were plotted:
\begin{itemize}
	\item The ratio of late to correct collisions and ratio of misses to total collision.
	\item The mean and $+/-2$ standard deviations of penetration time were plotted against each tolerance factor for each of the three tolerance values chosen.
\end{itemize}

@@

@@

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeLow}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. frame-time using a frame-time tolerance of $8ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeMid}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. frame-time using a frame-time tolerance of $15ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeHigh}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. frame-time using a frame-time tolerance of $25ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeHigh}
\end{figure}

>>>>

\subsubsection{Experiment parameters and output}
The two servers use the following tolerances unless otherwise stated: a maximum speed tolerance of $32m\mathord{\cdot}s^{-1}$; maximum latency tolerance of $2ms$; and a maximum frame-time tolerance of $15ms$. Each server has a random delay before starting between $0$ and the target frame-time in order to prevent the two servers always having synchronous update cycles. Each experiment is repeated $50$ times. An experiment was carried out for each aura tolerance value. The aura size for the varying tolerances are plotted and the tolerances used are marked. For each experiment, three tolerances values were chosen. For each tolerance value, the following output graphs were plotted:
\begin{itemize}
	\item The ratio of late to correct collisions and ratio of misses to total collision.
	\item The mean and $+/-2$ standard deviations of penetration time were plotted against each tolerance factor for each of the three tolerance values chosen.
\end{itemize}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{SpeedAuraSizes}
	\caption{Size of aura vs. speed tolerance. The speed tolerances used are marked in dashed lines}
	\label{fig_SpeedAuraSize}
\end{figure}

Fig. \ref{fig_SpeedAuraSize} shows the size of the aura (not including the bounding sphere of the object) vs increasing speed tolerance, calculated using equation \ref{auraEquation}.
The aura size increases continuously with speed, therefore we expect late collisions to begin immediately once the the speed tolerance is exceeded. False-positives are expected due to the frame-time delay method and should increase as speed increases.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{LatencyAuraSizes}
	\caption{Size of aura vs. latency tolerance. The latency tolerances used are marked in dashed lines}
	\label{fig_LatencyAuraSize}
\end{figure}

Fig. \ref{fig_LatencyAuraSize} shows the size of the aura (not including the bounding sphere of the object) vs increasing latency tolerance, calculated using equation \ref{auraEquation}. The aura size increases discretely with latency tolerance, therefore we expect late collisions to begin one the aura size required for the latency is higher than what is needed for the tolerance. In the latency tolerance experiments, this will be when latency reaches $3ms$ for the $2ms$ tolerance experiments and $20ms$ for $15ms$ tolerance experiment. Note that late collisions are not expected for the $8ms$ experiment, as $20ms$ latency is not reached. False-positives are expected due to the frame-time delay method and should increase as latency increases.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{FrameAuraSizes}
	\caption{Size of aura vs. frame-time tolerance. The frame-time tolerances used are marked in dashed lines}
	\label{fig_FrameTimeAuraSize}
\end{figure}

Fig. \ref{fig_FrameTimeAuraSize} shows the size of the aura (not including the bounding sphere of the object) vs increasing frame-time tolerance, calculated using equation \ref{auraEquation}. The aura size increases discretely with frame-time tolerance, therefore we expect late collisions to begin one the aura size required for the latency is higher than what is needed for the tolerance. In the varying frame-time experiments, this will be when frame-time reaches $16ms$ for the $8ms$ and $15ms$ tolerance experiments and $32ms$ for the $32ms$ tolerance experiment. Note that late collisions are not expected for the $8ms$ experiment, as $16ms$ frame-time is not exceeded. False-positives are expected due to the frame-time delay method and should increase as frame-time increases.

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeLow}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. frame-time using a frame-time tolerance of $8ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeMid}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. frame-time using a frame-time tolerance of $15ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeHigh}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. frame-time using a frame-time tolerance of $32ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeHigh}
\end{figure}
